Giant Low Surface Brightness Galaxies As Merger Remnants

### 2016-08-07 glsb.tex
update Victor status and funding
changed affiliation + typo

\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{1}, Victor P. Debattista\altaffilmark{3}
  }

\altaffiltext{1}{Department of Astronomy, University of Washington, Box 351580,
Seattle WA, 98195}
\altaffiltext{2}{University of Michigan}
\altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.  RCUK Fellow}
\altaffiltext{4}{California Institute of Technology}

@@

Observations of Malin~1 support the accretion model of GLSBs.  \citet{Barth07} analyze HST imaging of Malin~1 and find that the central object is well described as a normal early-type barred galaxy that was previously unresolved in ground-based imaging. \citet{Barth07} points out that extended disk structures in galaxies such as M31 appear to be a smooth continuation of the inner disk \citep{Ferguson02}, while Malin~1's extended disk is better described as a distinct component, (although \citet{Ibata05} claim M31's extended disk is of accretion origin).

@@

%--------------------------------------
\acknowledgments
Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs. Thanks to Dmitry Bizyaev for stimulating conversations about GLSBs. Thanks to Lauren MacArthur for discussions on stellar metallicity gradients.
%Thanks to the observing specialists at Apache Point for their help executing our remote observations.

>>>>

\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{5}, Victor P. Debattista\altaffilmark{3}
  }

\altaffiltext{1}{Department of Astronomy, University of Washington, Box 351580,
Seattle WA, 98195}
\altaffiltext{2}{University of Michigan}
\altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.}
\altaffiltext{4}{California Institute of Technology}
\altaffiltext{5}{Center for the Exploration of the Origin of the Universe
(CEOU), Department of Physics \& Astronomy, Seoul
National University, Seoul 151-742, Republic of Korea}

@@

Observations of Malin~1 support the accretion model of GLSBs.  \citet{Barth07} analyzes HST imaging of Malin~1 and find that the central object is well described as a normal early-type barred galaxy that was previously unresolved in ground-based imaging. \citet{Barth07} points out that extended disk structures in galaxies such as M31 appear to be a smooth continuation of the inner disk \citep{Ferguson02}, while Malin~1's extended disk is better described as a distinct component, (although \citet{Ibata05} claim M31's extended disk is of accretion origin).

@@

%--------------------------------------
\acknowledgments
Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs. Thanks to Dmitry Bizyaev for stimulating conversations about GLSBs. Thanks to Lauren MacArthur for discussions on stellar metallicity gradients.

VPD is supported by STFC Consolidated grant \#ST/M000877/1.
